
\documentclass[a4paper,30pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{helvet}
% Adjust margins
\usepackage[bottom=0in,top=1in]{geometry}

\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.9in}
\addtolength{\textheight}{1in}
\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-15pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\normalsize{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \vspace{-1pt}
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-3pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeItemTitle}[0]{}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Om Hemantkumar Purohit}} & \href{mailto:omhpurohit@gmail.com}{omhpurohit@gmail.com}\\
  \href{https://www.linkedin.com/in/om-purohit-957187175/}{Linkedin} & +1-716-235-9016 \\
\end{tabular*}

%----------- EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The State University Of New York, Buffalo}{NY, USA}
      {Master in Engineering Science}{Aug 2021 - Dec 2022}    
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, India}
      {Bachelor of Technology - Information Technology}{Jun 2017 - Jun 2021}
    \resumeSubHeadingListEnd
    
%----------- EDUCATION END -----------------
	    
\vspace{-5pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Python, Java, Javascript, Typescript, Matlab, SQL}
	\resumeSubItem{Frameworks}{Flask, Express, Spring Boot, React, Angular}
	\resumeSubItem{Databases}{MySQL, PostgreSQL, MongoDB, PouchDB, Neo4J}
	\resumeSubItem{Deployment}{Heroku, AWS, git, Azure, Docker, Kubernetes}
	\resumeSubItem{Visualization}{D3.js, Dash/Plotly, Altair, Matplotlib, Bokeh}
\resumeSubHeadingListEnd

% ----- EXPERIENCE START -----

\vspace{1pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{IQVIA}{Buffalo, NY}
    {Software Developer Intern}{May 2022 - Dec 2022}
    \resumeItemListStart
        \resumeItemWithoutTitle - Constructed the asynchronous microservice backend with Python, Flask and PostgreSQL. Deployed it via Kubernetes.
        \resumeItemWithoutTitle - Learned to develop with Java, Springboot. Applied Spring JPA, Hibernate to create an ORM for the backend. Tested
application using JUnit.
        \resumeItemWithoutTitle - Designed responsive and state persistent UI with React, Javascript, NodeJs, Redux and react-router.
        \resumeItemWithoutTitle - The application automated the installation tasks and reduced time from 5 hours to 10 minutes.
        \resumeItemWithoutTitle -  Contributed on the UI for data acquisition team using Angular 2, Material UI, and Typescript.

    \resumeItemListEnd
\vspace{1 pt}
    \resumeSubheading {Twimbit}{Delhi, India}
		{Developer Intern}{Aug 2020 - May 2021}		
		\resumeItemListStart
		    \resumeItemWithoutTitle - Developed Chrome extension to replace the default chrome history structure, storing the data in Neo4j.
            \resumeItemWithoutTitle - Designed a dashboard with D3.js, HTML and CSS, featuring chrome history as a hierarchical tree data structure.
            \resumeItemWithoutTitle - Built a dashboard using Pandas, Python, Dash/Plotly library to visualise tabs as clusters by performing topic modelling.
            \resumeItemWithoutTitle - Constructed an ETL pipeline with Python, Pandas, Selenium and Apache Superset with a scheduled scraping
            microservice.
            \resumeItemWithoutTitle - Utilized the stored pool of chrome history objects, implemented a search suggestion algorithm. Aiding researchers to quickly reach sites pertaining to their research topic.

		\resumeItemListEnd

\vspace{1pt}	
\resumeSubheading{Amilcar Technologies}{Johannesburg, South Africa}
    {Data Science Intern}{May 2020 - July 2020}
    \resumeItemListStart
        \resumeItemWithoutTitle - Developed a resume parser using pattern matching algorithms with a backend REST API leveraging Flask and Python.
        \resumeItemWithoutTitle - Built the UI using ReactJS with optimized search algorithms for recruiters to skim through seamlessly.
        \resumeItemWithoutTitle - Devised scrapers using Python, Selenium, Pandas, and BeautifulSoup that scraped 45k apps.
    \resumeItemListEnd
\vspace{1pt}	
\resumeSubheading{RMInfonetwork}{Vadodara, India}
    {Web Developer Intern}{May 2019 - July 2019}
    \resumeItemListStart
        \resumeItemWithoutTitle - Assembled various web applications for various clients and enterprises. Deployed them on AWS, Heroku, and GoDaddy.
        \resumeItemWithoutTitle - Used core web technologies to integrate frontend with PHP and XAMP Server. 
    \resumeItemListEnd
\vspace{1pt}
\resumeSubHeadingListEnd

\vspace{-5pt}

% ----- EXPERIENCE END -----
%-----------PROJECTS-----------------

\section{Projects}
\resumeSubHeadingListStart
\vspace{2pt}
\resumeSubItem{RAFT Consensus | Docker, Javascript, Express, MongoDB}{Implemented the famous consensus algorithm of RAFT, using socket and asynchronous programming
methodologies. Utilized javascript, NodeJs, express and docker to design the backend logic. }
\vspace{2pt}
\resumeSubItem{Indian Cuisine  \href{http://indiancuisineskaggle.com/}{(Link)}| React, Javascript, Express, Pouchdb, AWS Lightsail}{Developed an application to search and explore the Indian Cuisines Kaggle dataset. Built React components
integrated with NodeJs and Express in the backend. Managed and merged raw JSON data into a NoSQL database called PouchDB. Deployed on AWS LightSail.}
\vspace{2pt}
\resumeSubItem{Graphical Resume  \href{https://omegaji.github.io/Graphical-Resume/}{(Link)} | React, Javascript, D3.js}{Reconstructed my resume as a connected acyclic graph using D3.js and React. Implemented zooming, searching, SVG scaling and panning algorithms to efficiently navigate the whole visualization.  }
\vspace{2pt}
\resumeSubItem{AWS Image Recognition and Notification | S3, SNS, Lambda, Python, CloudWatch}{Leveraged AWS Rekognition, S3, and SNS to parse images and notify end users. Built a responsive UI with React connecting this microservice with AWS Lambda and Boto3.
}
\resumeSubHeadingListEnd

\end{document}
